Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-06-23 tensor/draft/draft-tensor-op.tex
[tensor/draft] updated values for tensor and scalar scenario, added A_FB's for B->K* ll, other small changes

\author{Stephan Jahn}
\affiliation{
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry $A_{\rm FB}^\ell$ and a flat
  term $F_H^\ell$ that are both suppressed in the standard model and very
  sensitive to nonstandard tensorial and scalar contributions. We use latest
  experimental results for $\ell = \mu$ in combination with $B_s\to \bar\mu\mu$
  to derive stronger model-independent constraints on tensorial and scalar
  effective couplings and determine their impact on $B\to K^*\bar\mu\mu$
  angular observables. Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings.
\end{abstract}

@@

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$ and the
treatment of theory uncertainties are relegated to appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{align}
  \label{eq:Heff}
  {\cal L}_{\rm eff} & =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, V_{tb}^{} V_{ts}^\ast
       \sum_{\ell = e, \mu,\tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i + \text{h.c.}
\end{align}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$)
operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$.
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which in principle could also give additional $\cos\theta_\ell$ dependence
to the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background.

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

To illustrate the sensitivity of $F_H^\ell$ to tensorial couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
the sensitivity to tensorial couplings is highest for $F_H^\ell$ at high $q^2$,
also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensorial couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of
tensorial couplings. Moreover, the dependence on vectorial couplings is such that
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

@@

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio and the rate CP asymmetry
of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the
imaginary parts of vectorial couplings.

@@

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ and
their tiny SM predictions. Thus our main objective is the derivation of stronger
constraints on tensorial and scalar couplings, taking advantage of their enhancement
in both observables over vectorial ones. For this purpose, we will consider several
model-independent scenarios, starting from rather restricted to more general ones,
in order to asses the effect of cancellations due to interference of various
contributions.

We will start with the scenario of only tensorial couplings and see that they are
well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and
$B_s \to \bar\mu\mu$. Here we find that for the first time all scalar couplings
can be bounded simultaneously by the combination of both measurements. Eventually
we will consider as a special scenario the SM
augmented by dimension six operators as an effective theory of new physics below
some high scale $\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
also interference effects with new physics in vectorial couplings. Finally, we
conclude this section with postdictions of the allowed ranges of the yet not
measured angular observables in $B\to K^*\bar\mu\mu$ given all other experimental
constraints.
\todo{Perhaps give also postdictions for $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
  }
\end{table*}

>>>>

\author{Stephan Jahn}
\affiliation{
  \todo{neue Adresse}
  Excellence Cluster Universe,
  Technische Universit\"at M\"unchen,
  Garching, Germany
}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry, $A_{\rm FB}^\ell$, and a flat
  term, $F_H^\ell$, that are strongly suppressed in the standard model. In both,
  nonstandard tensorial and scalar contributions are enhanced with respect
  to vectorial ones. We use latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive stronger model-independent 
  constraints on tensorial and scalar effective couplings and determine their 
  impact on not yet measured angular observables in 
  $B\to K^*\bar\mu\mu$, which feature the same suppression of vectorial couplings. 
  Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously
  upper bounds on all four couplings.
\end{abstract}

@@

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$, the
branching fraction of $B_s\to \bar\mu\mu$ and the
treatment of theory uncertainties are relegated to appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ C_7 \Op_7 + C_{7'} \Op_{7'}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$)
operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which will modify the simple $\cos\theta_\ell$ dependence
of the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background\footnote{The leading
QED corrections to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
corresponding effects in $B\to K \bar\ell\ell$.}.

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various
  $b\to s \bar\mu\mu$ decays that enter the fits with respective kinematics
  and experiments that provide the measurements. LCSR and lattice results of
  $B\to K^{(*)}$ form factors are used to constrain parameters of their
  $q^2$-dependence.
  For more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

To illustrate the sensitivity of $F_H^\ell$ to tensorial couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
the sensitivity to tensorial couplings is highest for $F_H^\ell$ at high $q^2$,
also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensorial couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of
tensorial couplings. Moreover, the dependence on vectorial couplings is such that
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

@@

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vectorial couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio, the lepton forward-backward
asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
additional constraints on the real and imaginary parts of vectorial couplings.

@@

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in 
$B^+ \to K^+ \bar\mu\mu$ and
their tiny SM predictions. Thus our main objective is the derivation of stronger
constraints on tensorial and scalar couplings, taking advantage of their enhancement
in both observables over vectorial ones. For this purpose, we will consider several
model-independent scenarios, starting from rather restricted to more general ones,
in order to asses the effect of cancellations due to interference of various
contributions.

We will start with the scenario of only tensorial couplings and see that they are
well constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and
$B_s \to \bar\mu\mu$. Here we find that for the first time all scalar couplings
can be bounded simultaneously by the combination of both measurements. Eventually
we will consider as a special scenario the SM
augmented by dimension six operators as an effective theory of new physics below
some high scale $\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
as in the SM, i.e. $v \ll \Lambda_{\rm NP}$. For each scenario, we investigate
also interference effects with new physics in vectorial couplings. Finally, we
conclude this section with postirior predictions of the allowed ranges of the yet
not measured angular observables in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in 
$B_s\to\bar\mu\mu$ given all other experimental constraints.

\todo{Explain special initialisation of Markov chains at fixed point in parameter
space in order to avoid other local modes in subspace of nuisance parameters.
What would be appropriate place to do so?}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.32,\, 0.16]$ ($[-0.52,\, 0.35]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & $\quad$ $[-0.23,\, 0.14]$ ($[-0.39,\, 0.30]$) $\quad$
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & $[-0.17,\, 0.22]$ ($[-0.33,\, 0.37]$)
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & $[-0.18,\, 0.16]$ ($[-0.32,\, 0.32]$)
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.44,\, 0.45]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & $[-0.20,\, 0.18]$ ($[-0.36,\, 0.35]$)
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.43]$ ($[0.03,\, 0.57]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & $[0.10,\, 0.33]$ ($[0.02,\, 0.43]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also complex-valud new physics contributions to $\wilson{9,\,10}$.
  }
\end{table*}
